Global code motion of congruent instructions

### 2017-04-18 paper.tex
fix page layout
removed redundancy

After no more candidates are hoistable, sinking is performed. Sinking is only
performed once becase currently there are very few sinkable candidates
(Table~\ref{tab:code-motion-metric}) as SimplifyCFG of LLVM (which runs before
\GCM{}) has a code-sinking which already sinks several instructions.

@@

Code size also remained almost the same as a result of \gcm{} as shown in
Table~\ref{tab:code-size}.  The code size listed here is the text size (from
linux size command) of the final executables for each benchmark.  Some bencmarks
like 473.astar increased in code size by almost 2\%. This is because once the
code-size of a function decreases (due to \GCM{}), it becomes cheaper to inline. As
we can see in Table-\ref{tab:stats}, four more functions got inlined in
473.astar. Except for 447.dealII, 450.soplex, 482.sphinx3 and 483.xalancbmk all
other benchmarks got more functions inlined.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|r|r|r|}
      \hline
Number of spills  &base(-Ofast) &\GCM{}(-Ofast) &\%change (low better) \\\hline
400.perlbench	  & 2539	& 2493	& 0.98 \\\hline
401.bzip2	  & 718	        & 707	& 0.98 \\\hline
403.gcc	          & 5782	& 5722	& 0.99 \\\hline
429.mcf	          & 14	        & 17	& 1.21 \\\hline
433.milc	  & 635	        & 642	& 1.01 \\\hline
444.namd	  & 3223	& 3274	& 1.01 \\\hline
445.gobmk	  & 2166	& 2173	& 1.00 \\\hline
447.dealII	  & 11074	& 10234	& 0.92 \\\hline
450.soplex	  & 1122	& 1125	& 1.00 \\\hline
453.povray	  & 4701	& 4692	& 1.09 \\\hline
456.hmmer	  & 1197	& 1274	& 1.06 \\\hline
458.sjeng	  & 168	        & 176	& 1.05 \\\hline
462.libquantum	  & 118	        & 118	& 1.00 \\\hline
464.h264ref	  & 3379	& 3454	& 1.02 \\\hline
470.lbm	          & 33	        & 33	& 1.00 \\\hline
471.omnetpp	  & 524	        & 527	& 1.00 \\\hline
473.astar	  & 180	        & 201	& 1.12 \\\hline
482.sphinx3	  & 674	        & 670	& 0.99 \\\hline
483.xalancbmk	  & 5102	& 4965	& 0.97 \\\hline
Grand Total	  & 43349	& 42497	& 0.98 \\\hline
    \end{tabular}
  \end{center}
  \caption{Number of spills before and after \gcm{}(\GCM{}) on SPEC2006 at -Ofast}
  \label{tab:spills}
\end{table}

@@

While benchmarking \SPEC{} we see both increase as well as decrease in
the codesize of the final binaries. Since the pass runs early, it affects many
optimizations which rely on the number of instructions, length of the use-def
chain, and other metrics. For instance, the inliner is impacted by a decrease in
the number of instructions in the caller and callee, as its heuristics estimate
the size of functions to be inlined.

>>>>

\newpage
After no more candidates are hoistable, sinking is performed. Sinking is only
performed once becase currently there are very few sinkable candidates
(Table~\ref{tab:code-motion-metric}) as SimplifyCFG of LLVM (which runs before
\GCM{}) has a code-sinking which already sinks several instructions.

@@

Code size also remained almost the same as a result of \gcm{} as shown in
Table~\ref{tab:code-size}.  The code size listed here is the text size (from
linux size command) of the final executables for each benchmark.  Some bencmarks
like 473.astar increased in code size by almost 2\%. This is because once the
code-size of a function decreases (due to \GCM{}), it becomes cheaper to
inline. As we can see in Table-\ref{tab:stats}, four more functions got inlined
in 473.astar. Except for 447.dealII, 450.soplex, 482.sphinx3 and 483.xalancbmk
all other benchmarks got more functions inlined. Also, since the pass runs
early, it affects many optimizations which rely on the number of instructions,
length of the use-def chain, and other metrics.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|r|r|r|}
      \hline
Number of spills  &base(-Ofast) &\GCM{}(-Ofast) &\%change (low better) \\\hline
400.perlbench	  & 2539	& 2493	& 0.98 \\\hline
401.bzip2	  & 718	        & 707	& 0.98 \\\hline
403.gcc	          & 5782	& 5722	& 0.99 \\\hline
429.mcf	          & 14	        & 17	& 1.21 \\\hline
433.milc	  & 635	        & 642	& 1.01 \\\hline
444.namd	  & 3223	& 3274	& 1.01 \\\hline
445.gobmk	  & 2166	& 2173	& 1.00 \\\hline
447.dealII	  & 11074	& 10234	& 0.92 \\\hline
450.soplex	  & 1122	& 1125	& 1.00 \\\hline
453.povray	  & 4701	& 4692	& 1.09 \\\hline
456.hmmer	  & 1197	& 1274	& 1.06 \\\hline
458.sjeng	  & 168	        & 176	& 1.05 \\\hline
462.libquantum	  & 118	        & 118	& 1.00 \\\hline
464.h264ref	  & 3379	& 3454	& 1.02 \\\hline
470.lbm	          & 33	        & 33	& 1.00 \\\hline
471.omnetpp	  & 524	        & 527	& 1.00 \\\hline
473.astar	  & 180	        & 201	& 1.12 \\\hline
482.sphinx3	  & 674	        & 670	& 0.99 \\\hline
483.xalancbmk	  & 5102	& 4965	& 0.97 \\\hline
Grand Total	  & 43349	& 42497	& 0.98 \\\hline
    \end{tabular}
  \end{center}
  \caption{Number of spills before and after \gcm{}(\GCM{}) on SPEC2006 at
    -Ofast. Spills reduced by 2\% overall.}
  \label{tab:spills}
\end{table}

@@
